Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
Rough future directions done.

\subsection{Privacy for Smartphones and Wearables}
Mention Adrienne's work here, and other cool smartphone studies of any sort. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.

@@

\subsection{Ubiquitous Computing}

\subsection{User Perception}
Mention how people are generally really bad at estimating the likelihood of some threat or event occurring. And since

@@

\subsection{Threat Landscape Investigation} 
(REDO) To generate the list of possible scenarios which can happen with a wearable device, we did three things. Firstly, we looked at the most popular list of wearable technologies (including the Fitbit fitness tracker, Pebble smartwatch, and Glass wearable computing device) and their sensors and capabilities. Secondly, we looked at past research in mobile devices, vision videos for wearables, and the news for possible concerns.

Write about how I came up with the questions, what was considered (looking at many wearable devices and possible sensors, looking through previous works, just thinking of as many as possible), and the final list.

Talking about the focus group here. Does this even need to happen?

@@

\subsection{Future Research Directions}
<ask David's/Serge's input for this section>

@@

I messed up that motorcycle question.

>>>>

\subsection{Privacy for Smartphones and Wearables}
(REDO) Mention Adrienne's work here, and other cool smartphone studies of any sort. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.

@@

\subsection{Ubiquitous Computing}
(REDO) As technology becomes more and more ubiquitous, more sensors will record more things about more people more of the time. There are an endless amount of unique situations which can negatively impact a person's privacy or security. There is a clear need to better communicate these risks to people (cite webcam paper and other papers here?), but there are too many things to warn people about. Therefore, we need to know what are the most threatening and also most relevant situations to inform the users about, since we can't bug them all the time about everything.

\subsection{User Perception}
(REDO) In this paper, we investigate one of the two important questions--what are the most relevant situations to people. We do this firstly because people are really bad at knowing the likelihood of something, especially a threat with respect to security or privacy, is going to happen (sources here). And while the most damaging situations should also be addressed, this is not yet possible since these technologies haven't been adopted and the damage hasn't happened, so we don't know yet. Additionally, since the number one concern that people had with these devices was privacy (can I say result here? I guess I already did in abstract), we need to know what people consider private, which is more nuanced and requires a user study like this survey.

@@

\subsection{Threat Landscape Investigation} 
(REDO) To generate the list of possible scenarios which can happen with a wearable device, we did three things. Firstly, we looked at the most popular list of wearable technologies (including the Fitbit fitness tracker, Pebble smartwatch, and Glass wearable computing device) and their sensors and capabilities. Secondly, we looked at past research in mobile devices and current wearable device considerations. Thirdly, we finished off brainstorming possible things yet to come by looking at vision videos for wearables, and the news for possible concerns.

Motivate the fact that this is important here! Mention ubiquitious computing, preventing security threats, etc.

@@

\subsection{Future Research Directions}
(REDO, ask David's/Serge's input for this section) Additional future work is encouraged in the area of studying privacy with respect to ubiquitous computing, since we proved it was the number one concern of the users of wearable devices. Clearly, this is a hard question which has been worked on for a long time but not yet fully addressed. Even this survey just barely touched on the various factors which can influence privacy perceptions and how upset people would be.

 Also, maybe some work with respect to security threats, and how feasible they might be, and some defenses against stopping wearables devices from getting sensitive information (like blocking text, detecting sensitive situations like the bathroom, etc.). Research which defends against false information, false positive commands, and just more safeguards against the new system for wearables, whatever that is, is also something to really look into.

 Work making sure that people are aware of what is going on, using indicators, not-too-transparent interfaces, and maybe being polite (recording rules follow social rules--think polite glass talk from Jaeyeon at MSR) are going to be valuable as wearables get more sophisticated but also more adopted by people. Think about it--put people in control of the technology, not technology shifting the social norms (our survey says that one of the top concerns of people were about how wearables will change social norms).

@@

(REDO, Should I even say this?) I messed up that motorcycle question. I wish I actually had a calibration point for high risk high benefit for the Fischoff technology assessment questions. But well, none of the new technologies fit that description so we didn't really need it critically.
